%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Amir CV/Resume
% XeLaTeX Template
% Version 1.0 (5/5/2014)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Amir Suhail
% With extensive modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[letterpaper]{amir-resume} % Use US Letter paper, change to a4paper for A4
\usepackage[document]{ragged2e}
\usepackage[none]{hyphenat}
\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

\lastupdated % Print the Last Updated text at the top right

\namesection{Amir}{Suhail}{ % Your name
\href{mailto:suhailamir094@gmail.com}{suhailamir094@gmail.com} | 8475003268 % Your contact information
}

%----------------------------------------------------------------------------------------
%	LEFT COLUMN
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page

%------------------------------------------------
% Education
%------------------------------------------------

\section{Education}

\subsection{JECRC University}

\descript{B.Tech in Computer Science}
\location{Completed May 2016 | Jaipur, Rajasthan \\ Cum. CGPA: 8.0/10}

\sectionspace % Some whitespace after the section

%------------------------------------------------

\subsection{Maria Assumpta Convent }

\location{Grad. May 2012 | Kashipur, Uttarakhand}

\sectionspace % Some whitespace after the section

%------------------------------------------------
% Links
%------------------------------------------------

\section{Links}

Github:// \href{https://github.com/suhailamir94}{\bf suhailamir94} \\
LinkedIn:// \href{https://www.linkedin.com/in/amir-suhail-02b19bbb}{\bf amir-suhail-02b19bbb} \\
\sectionspace % Some whitespace after the section

%------------------------------------------------
% Skills
%------------------------------------------------

\section{Skills}

\subsection{Programming}

\location{Over 5000 lines:}
JavaScript \textbullet{} Node.js \textbullet{} Express.js \\
Hyperledger Fabric  \textbullet{} React.js  \\
React Native  \textbullet{} Expo \textbullet{} MongoDB

\sectionspace % Some whitespace after the section

%------------------------------------------------
% Awards
%------------------------------------------------

\section{Awards}

Employee of the Month - June 2018 \\
Employee of the Month - Nov 2018
\sectionspace % Some whitespace after the section

%----------------------------------------------------------------------------------------

\end{minipage} % The end of the left column
\hfill
%
%----------------------------------------------------------------------------------------
%	RIGHT COLUMN
%----------------------------------------------------------------------------------------
%
\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page

%------------------------------------------------
% Experience
%------------------------------------------------

\section{Experience}

\runsubsection{Accenture}
\descript{| Application Development Analyst}

\location{June 2018 – Present | Bangalore, Karnataka}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightitemize}
\item  {\bf Blockchain Postal Solution:}  \justifying Developed a web and mobile application using React.js/Expo to track all the postal packages being transferred between multiple countries. Implemented a Node.js SDK with US Post SSO using passport.js for adding and retrieving relevant data from Blockchain and MongoDB.
\item {\bf Blockchain Health care Solution:}  Developed a web application using React.js for multiple Blockchain participants i.e, Patient, Doctor, Pharmacy and Authority, each having a separate dashboard. The application used QR codes to track different medicines with features like displaying and scanning the QR codes. Implemented a Node.js SDK with Google/Facebook SSO using passport.js for adding and retrieving relevant data from Blockchain and MongoDB.
\end{tightitemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{Accenture}
\descript{| Application Development Associate}

\location{Nov 2016 – May 2018 | Bangalore, Karnataka}
\begin{tightitemize}
\item {\bf Supply Chain Blockchain Solution:}  \justifying Developed a web application using React.js for multiple Blockchain participants i.e, Manufacturer, Warehouse, Distributor and Pharmacy. The application displayed real time location, temperature, humidity and intrusion detection of the product being transferred. Implemented a Node.js SDK for adding and retrieving relevant data from Blockchain.
\item {\bf Certificate Management App: }   Developed a web application using React.js to upload and display certificates earned by Accenture employees. The application helped the employees to update their certificates at the time of appraisal . Also, Implemented a Node.js SDK for adding and retrieving relevant data from MySQL database.
\item {\bf IBM Bluemix Cloud OnBoarding App: }   Developed a web application using React.js to upload and display the requests for Bluemix Organisation/Space from different Accenture Projects. The application enabled the projects to add/delete requests for IBM Bluemix Cloud Space for their Projects .Also, Implemented a Node.js SDK for adding and retrieving relevant data from Cloudant database.
\item {\bf SlackBot/SkypeBot: }   Developed Node.js API's for virtual Assistants based on Slack and Skype. The chatbot were based on Accenture Virtual Assistant framework AFPVA. The Assistant helped the users to raise queries as well as  find status of their queries.
\end{tightitemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{QorQl}
\descript{| Application Development Intern}

\location{Jan 2016 – June 2016 | Noida, UP}
\begin{tightitemize}
\item {\bf QLive:}\justifying Developed a web application that showed the current live queue status at a doctor’s clinic. The application is still used by 50+ Doctors in Noida to show the live patient queue in their clinics.
\item {\bf QBiz: } Developed a web application used to locate every Doctor's clinic in Delhi-NCR on Google maps. The application was used by Qorql's marketing team to target potential clients.
\item {\bf QDoc: } Developed multiple Java Spring Boot API's to store and retrieve Doctor's/Patient's data in MongoDB.
\item {\bf QAsst: } Developed multiple Java Spring Boot API's to store and retrieve Patient's queue data from MongoDB.
\end{tightitemize}



\end{minipage} % The end of the right column

%----------------------------------------------------------------------------------------
%	SECOND PAGE (EXAMPLE)
%----------------------------------------------------------------------------------------

%\newpage % Start a new page

%\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page

%\section{Example Section}

%\end{minipage} % The end of the left column
%\hfill
%\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page

%\section{Example Section 2}

%\end{minipage} % The end of the right column

%----------------------------------------------------------------------------------------

\end{document}
